---
title: "Business Intelligence Lab Submission Markdown"
author: "<Team Marafiki>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** 
|                                                   |                                                                                                                                                                          |
|                                                   | 1.  136446 - C - Mirav Bhojani                                                                                                                                                 |
|                                                   |                                                                                                                                                                          |
|                                                   | 2.  136788 - C - Nyaga Derrick                                                                                                                                                 |
|                                                   |                                                                                                                                                                          |
|                                                   | 3.  136709 - C - Jane Mugo                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 4.  135399 - C - Sheila Kavinya                                                                                       

|
|                                                   | 5.  136895 - C - Wesley Wanyama                                                                                                                                                                         |
|                                                   |                                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | Team Marafiki                                                                                                       
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
## mlbench ----
if (require("mlbench")) {
  require("mlbench")
} else {
  install.packages("mlbench", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## readr ----
if (require("readr")) {
  require("readr")
} else {
  install.packages("readr", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## caret ----
if (require("caret")) {
  require("caret")
} else {
  install.packages("caret", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## e1071 ----
if (require("e1071")) {
  require("e1071")
} else {
  install.packages("e1071", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## factoextra ----
if (require("factoextra")) {
  require("factoextra")
} else {
  install.packages("factoextra", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}

## FactoMineR ----
if (require("FactoMineR")) {
  require("FactoMineR")
} else {
  install.packages("FactoMineR", dependencies = TRUE,
                   repos = "https://cloud.r-project.org")
}
```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console


Describe the code chunk here: The dataset was loadedto perform further analysis

```{student_performance_dataset <-
  readr::read_csv(
    "data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset.csv", # nolint}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
```

Describe the next code chunk here: This R code computes and applies a Box-Cox power transformation to the `student_performance_dataset`, stabilizing variance and enhancing normality for statistical analysis.

```{ summary(student_performance_dataset)


model_of_the_transform <- preProcess(student_performance_dataset, method = c("BoxCox"))
print(model_of_the_transform)
student_performance_dataset_box_cox_transform <- predict(model_of_the_transform, # nolint
                                                         student_performance_dataset)
summary(student_performance_dataset_box_cox_transform)
}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```